\section*{Problem 7-4 Random Failures in Uncorrelated Networks}

Compute the critical threshold $f_c$ for each of the following degree distributions, under the assumption that the
networks do not exhibit any degree correlation.

\begin{enumerate}
	\item Poisson distribution, i.e.,
	
	\begin{equation*}
		p_k = e^{-\mu}\frac{\mu^k}{k!}
	\end{equation*}

	\item Discrete exponential distribution, i.e.,
	
	\begin{equation*}
		p_k = (1 - e^{-\lambda})e^{-\lambda k}
	\end{equation*}

	\item Dirac delta distribution, i.e.,
	
	\begin{equation*}
		p_k = \delta_{k,k_0} = 
		\begin{cases}
			1 & \text{if $k = k_0$,} \\
			0 & \text{otherwise.}
		\end{cases}
	\end{equation*}
\end{enumerate}

\noindent
Discuss the consequences of your results for network robustness.

\noindent
\textit{Hint:} You may use the first and second moment from the lecture or other literature without a proof. \newline

\noindent
We know $f_c$ can be calculated by:

\begin{equation*}
	f_c = 1 - \frac{1}{\frac{\langle k^2 \rangle}{\langle k \rangle} - 1}
\end{equation*}

\begin{enumerate}
	\item For the poisson distribution, we receive:
	
	\begin{equation*}
		f_c = 1 - \frac{1}{\frac{\mu^2 + \mu}{\mu} - 1} = 1 - \frac{1}{\mu}
	\end{equation*}

	This means the higher $\mu$ the more robust the network is towards random failures. If $\mu \rightarrow \infty$ we receive maximum robustness as all nodes would theoretically need to fail for the network to be considered fragmented (even if this does not make sense since there would not be a network present anymore).

	\item For the discrete exponential distribution, we receive (using Wolfram Alpha):

	\begin{equation*}
			\langle k \rangle = \frac{(1 - e^{-\lambda})}{\lambda^2}
	\end{equation*}

	\begin{equation*}
		\langle k^2 \rangle = \frac{2(1 - e^{-\lambda})}{\lambda^3}
	\end{equation*}

	\begin{equation*}
		f_c = 1 - \frac{1}{\frac{2}{\lambda} - 1}
	\end{equation*}

	This means the lower $\lambda$ the more robust the network is towards random failures. If $\lambda \rightarrow 0$ we receive maximum robustness. 

	\item For the dirac delta distribution, we receive:

	\begin{equation*}
		f_c = 1 - \frac{1}{\frac{k_0^2}{k_0} - 1} =  1 - \frac{1}{k_0 - 1}
	\end{equation*}

	Similar to the poisson distribution, the dirac delta distribution becomes more robust towards random failures the higher $k_0$ is. This becomes maximum for clique like structures. 

\end{enumerate}