\section{Problem 1-3 Difficulty of an Exhaustive Search}

Approximate the number of walks that need to be checked for an Eulerian trail for the following settings:

\begin{enumerate}
	\item A complete graph with $N=4$ nodes. Recall that a graph is complete if there is an edge between every pair of nodes in N, i.e., we have a clique.
	
	An undirected clique with $N=4$ nodes has $L=\frac{N(N-1)}{2}=6$ edges. Thus an Eulerian trail in such a graph would have a length of $l=6$. The number of walks $W=(n_0, ..., n_l)$ that need to be checked being a potential Eulerian trail is therefore $4 \cdot 3^{6}=2.916$.
	
	\item A regular graph with $N$ nodes and where each node has exactly $k$ links (that is why such a graph is called regular). The resulting formula should depend on $k$. By replacing $k$ with $\langle k \rangle$ one can get an estimate for the number of walks of length $K$ in a generic graph with $N$ nodes and $K$ links.
	
	A regular graph with $N$ and $k$ links per node has $L=\frac{N \cdot k}{2}$ edges. Thus an Eulerian trail in such a graph would have a length of $l=\frac{N \cdot k}{2}$. The number of walks $W=(n_0, ..., n_l)$ that need to be checked being a potential Eulerian trail is therefore $N \cdot k^{\frac{N \cdot k}{2}}$.
	
	\item Use your results from part 2., based on $\langle k \rangle$, to compute the approximate number of walks for the bridges of K\"onigsberg (see Figure 1).
	
	The average degree in the seven bridges of K\"onigsberg problem is $\langle k \rangle = \frac{2L}{N} = 3,5$. Thus the approximate number of walks to be checked is $N \cdot \langle k \rangle^{\frac{N \cdot \langle k \rangle}{2}} = 4 \cdot 3,5^{\frac{4 \cdot 3,5}{2}} \approx 25.735,72$.
	
	\item The historical part of Venice has 428 bridges. Assuming that $\langle k \rangle = 2$, how many walks have to be checked for being an Eulerian trail?
	
	The historical part of Venice has $N=\frac{2L}{\langle k \rangle}=428$ nodes. Thus the approximate number of walks to be checked is $N \cdot \langle k \rangle^{\frac{N \cdot \langle k \rangle}{2}} = 428 \cdot 2^{\frac{428 \cdot 2}{2}} \approx 2,97 \cdot 10^{131}$. 
	
\end{enumerate}