\section{Problem 6-1 The $t$-Party Evolving Network Model}

At the $t$-party gender plays no role, hence each newcome is allowed to invite \textbf{exactly} one other participant to a dance. However, attractiveness plays a role: More attractive participants are more likely to be invited to a dance
by a new participant. The party evolves following these rules:

\begin{itemize}
	\item Every participant corresponds to a node $i$ and is assigned a time-independent attractiveness coefficient $\eta_i$.
	\item At each time step a new node joins the $t$-party.
	\item This new node then invites one already partying node to a dance, establishing a new link with it.
	\item The new node chooses its dance partner with probability proportional to the potential partner's attractiveness. If there are $t$ nodes already at the party, the probability that node $i$ receives a dance invitation is:
	
	\begin{equation*}
		\Pi_i = \frac{\eta_i}{\sum_{j}^{} \eta_j} = \frac{\eta_i}{t \langle \eta \rangle}
	\end{equation*}

	where $\langle \eta \rangle$ is the average attractiveness.
\end{itemize}

\begin{enumerate}
	\item Derive the time evolution of the node degrees, telling us how many dances a node had.
	
	The rate at which an existing participant $i$ acquires dance partners is
	
	\begin{equation*}
		 \frac{dk_i}{dt} = 1 - (1 - \Pi(\eta_i)).
	\end{equation*}

	Using a series expansion and mean-field approximation we receive for $t \rightarrow \infty$
	
	\begin{equation*}
		\frac{dk_i}{dt} \approx \frac{\eta_i}{\sum_{j=1}^{N-1} \eta_j} = \frac{\eta_i}{t \langle \eta \rangle}.
	\end{equation*}

	By integrating 
	
	\begin{equation*}
		dk_i = \frac{\eta_i}{\langle \eta \rangle} \frac{dt}{t} \Rightarrow \int_{1}^{k_i(t)} dk_i = \frac{\eta_i}{\langle \eta \rangle} \int_{t_i}^{t} \frac{1}{t} dt
	\end{equation*}

	we obtain
	
	\begin{equation*}
		k_i(t, \eta_i) = \frac{\eta_i}{\langle \eta \rangle} \cdot ln(\frac{t}{t_i}) + 1.
	\end{equation*}
	
	\item Derive the degree distribution of nodes with attractiveness $\eta$.
	
	To build the cumulative degree distribution function, we first need to derive the time constraint when a participant should have entered the $t$-party the earliest to have at most $k$ dances.
	
	\begin{equation*}
		\begin{split}
			k_i(t, \eta_i) = \frac{\eta_i}{\langle \eta \rangle} \cdot ln(\frac{t}{t_i}) + 1 < k \\
			t_i > t - e^{\frac{(k - 1) \langle \eta \rangle}{\eta_i}}
		\end{split}
	\end{equation*}

	We know that the number of such participants (here as a continuous number) who had at most $k$ dances is given by $N_{<k} = t - t_i$ (as only one participant joins the $t$-party at every time step) with $t_i$ being derived from the above time constraint. Thus the cumulative degree distribution function is given by
	
	\begin{equation*}
		\begin{split}
			P(k_i < k) = \frac{N_{<k}}{N} = \frac{1}{t} \int_{\eta_{min}}^{\eta_{max}} e^{\frac{(k - 1) \langle \eta \rangle}{\eta}} d\eta.
		\end{split}
	\end{equation*}
	
	Note that we needed to average over the fitness/attractiveness distribution and that $N \approx t$ for $t \rightarrow \infty$. 
	
	To receive the degree distribution function we take the derivative of the cumulative degree distribution function and get
	
	\begin{equation*}
		\begin{split}
			p_k = \frac{dP(k)}{dk} = \frac{1}{t} \int_{\eta_{min}}^{\eta_{max}} \frac{\langle \eta \rangle}{\eta} e^{\frac{(k - 1) \langle \eta \rangle}{\eta}} d\eta.
		\end{split}
	\end{equation*}
	
	\item If half of the nodes have $\eta=2$, and the other half $\eta=1$ , what is the degree distribution of the network after a sufficiently long time?
	
	\begin{equation*}
		\begin{split}
			p_k = \frac{1}{t} (0.75e^{0.75(k - 1)} - 1.5e^{1.5(k - 1)}).
		\end{split}
	\end{equation*}

	Intuitively, there should only be very small degree nodes in the network as each dancers' fitness becomes neglectible if $t \rightarrow \infty$. This partly becomes visible in the above formula as the inverse relation from $p_k$ to $t$ pushes the probability of any degree node to 0. Of course this should not hold for small degree nodes, which is why we guess that there might still be an error in the formula of $p_k$. 
	
\end{enumerate}